%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{ff9900}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Rahul Kale}{}

\position{General Manager, Fulfillment Planning, John Deere India Pvt.
Ltd.}
\address{Pune, India}

\mobile{+91 77708 11127}
\email{\href{mailto:rahul.kale@gmail.com}{\nolinkurl{rahul.kale@gmail.com}}}
\github{r-kale}
\linkedin{rahul-kale-723a0720}
\twitter{rahulvilaskale}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {May, 2021}
    {Rahul Kale~~~·~~~Resume}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{summary}{%
\section{Summary}\label{summary}}

Supply Chain Professional with cross domain experience of over 17 years
with passion for leveraging technology to gain business edge.
Successfully established raw material supply chain at multiple
greenfield facilities that drove customer and product base expansion.

Leading Fulfillment Planning for India Factories driving end to end
planning by building alliance with senior leadership of Operations,
Finance and Marketing.

Actively guides a diverse team on forecasting and satisfying demand
through factory operation plans within bounds of constraint. Holds
responsibility of optimizing the product inventory and own product
inventory assets.

\hypertarget{skills-key-highlight}{%
\section{Skills \& Key Highlight}\label{skills-key-highlight}}

\begin{itemize}
\tightlist
\item
  \textbf{Change Management}\newline  \textit{Transforming a traditional planning business process to a responsive digital process aided by inhouse developed data driven tools.}
\item
  \textbf{Project Management}\newline  \textit{Leading critical subfunctions for concept to market product program implementation}
\item
  \textbf{Managing Disruption}\newline  \textit{Lead India Factory Planning during COVID challenges.}
\item
  \textbf{Inventory Management}\newline  \textit{Lead projects to balance demand variation with optimized assets.}
\item
  \textbf{Establish Product Supply Chain}\newline  \textit{Integrating complex supply chain from multiple countries for business start-up.}
\item
  \textbf{Influencing}\newline  \textit{Work with multiple stakeholders in complex projects}
\item
  \textbf{Reproducibility and Repeatability}\newline  \textit{Leverage technology to free up efforts. Focus on core issues. Reports create themselves; this resume is programmatically generated. 
  Code: \url{https://github.com/r-kale/rahul_kale_cv}}
\item
  \textbf{Digitization and optimization of business process}\newline  \textit{Drive multiple analytic projects to transform legacy process to data centric process adopted for flexible business needs}
\end{itemize}

\hypertarget{work-experience}{%
\section{Work Experience}\label{work-experience}}

\textbf{General Manager - Fulfillment Planning} \hfill John Deere India
Pvt Ltd - Pune\newline . \hfill Jan-2016 -
Current\newline \textit{- \hspace{5mm}  Leading a diverse team of 20 individuals. Managing a fulfillment planning vertical for pan, India integrated operations including \textbf{5 production factories} across two campus locations in India. Products include tractors from 28 HP to 130 HP for \textbf{India \& 110+ countries} globally. Planning for \textbf{1000+ fixed configurations and custom made unique} individual build tractors both for \textbf{build to stock and build to order} environment. Additionally plan for \textbf{international sourcing} of complex aggregate from India operations to sister units worldwide.\newline - \hspace{5mm}  Responsible  for \textbf{Sales and Operation Planning} of India factories.  Manage annual volume of \textbf{100K+ tractors with 30K+ complex aggregates} with overall \textbf{sales of over m\$1000+}. Oversee and support team to drive alliance with cross functional teams for the planning process.\newline - \hspace{5mm}  Guide the team for day to day production planning,  \textbf{balancing constraints and executing control over production}.\newline - \hspace{5mm}  Oversee \textbf{Complexity Management} on product offering, drive pruning of portfolio to limit product offering. For new product programs manage development of configurations and phase-in / out plans.\newline - \hspace{5mm}  \newpage  - \hspace{5mm} \textbf{Lead Asset Management and optimization} for Finish Good products owing a inventory with \textbf{annual average asset cost of over m\$100.}  Develop targets and metrics for Inventory control and planning. Collaborate with finance leadership on asset turns and with product marketing teams for inventory distribution.\newline - \hspace{5mm}  Part of  \textbf{Factory Leadership Council} contributing on strategic planning, initiatives and goal setting for factory teams. Responsible for  long term forecasting to support capacity planning.}
\newline \vspace{2mm} \newline
\textbf{Assistant General Manager - Supply Chain Management} \hfill John
Deere India Pvt Ltd - Dewas\newline . \hfill May-2013 -
Jan-2016\newline \textit{- \hspace{5mm}  Leading a team of 8 buyers and 40 warehouse staff for \textbf{establishing and executing supply chain procurement policies} and managing procurement with diverse and international Supply Base for commodities including Sheet Metal, Electrical, Hydraulic, Castings and Machining, Gear and Shafts, Hardware, Oil and Coolants among others. Managing annual \textbf{procurement in excess of m\$100.}\newline - \hspace{5mm}  Drive \textbf{warehousing strategy} for the new unit and leading the warehouse staff for developing warehouse plans including designing layouts and storage systems, replenishment systems, Kanban or 2-bin systems. Defining material handling needs and working on optimum layouts for reducing congestion. Management of Docks and receipt planning. Designing transport storage systems for optimized logistics cost. Support overall procurement and warehouse management of \textbf{over 3500+ unique parts.}}
\newline \vspace{2mm} \newline
\textbf{Executive Manager - Supply Chain Management} \hfill John Deere
India Pvt Ltd - Pune\newline . \hfill Jun-2009 -
May-2013\newline \textit{- \hspace{5mm}  Leading team of PDP SM engineers for managing development lifecycle from design drawings to PPAP of Sheet Metal components.\newline - \hspace{5mm}  Creating \textbf{Supply Chain strategy} for a new facility introducing a \textbf{completely unique product category}. Leading \textbf{Program Management} for Supply Chain portion of new product introduction.\newline - \hspace{5mm}  Defining costing norms, doing should-cost analysis and settling part cost with suppliers. Working on tool design, production process and establishing quality norms for regular procurement.}
\newline \vspace{2mm} \newline
\textbf{Manufacturing Design Engineer - Operations} \hfill John Deere
India Pvt Ltd - Pune\newline . \hfill May-2005 -
Jun-2009\newline \textit{- \hspace{5mm}  As a Industrial Engineer define line or station layout, work content, conduct time study and establish work norms.\newline - \hspace{5mm}  Engage with indirect suppliers for procurement of tools, machine and equipments for capital purchase and establish required manufacturing capacity.\newline - \hspace{5mm}  Work on EPDP process and Manufacturing Design engineer and lead through completion of all program execution phases.}
\newline \vspace{2mm} \newline
\textbf{Procurement Engineer - Supply Chain Management} \hfill John
Deere India Pvt Ltd - Pune\newline . \hfill Jun-2003 -
May-2005\newline \textit{- \hspace{5mm}  Defining Inventory DOH targets,  MRP parameters to \textbf{optimize procurement and minimize inventory.} Defining Cycle count process based on ABC categorization and \textbf{ensuring inventory accuracy.}}
\newline \vspace{2mm} \newline

\hypertarget{distinctive-mentions}{%
\section{Distinctive Mentions}\label{distinctive-mentions}}

\begin{itemize}
\tightlist
\item
  \textbf{2020 - Outstanding Team Award}\newline\textit{India Apex Award for best team, awarded for production recovery efforts after COVID disruption leading to record financial performance.}
\item
  \textbf{2019 - President Award of Excellence}\newline\textit{Global Enterprise Aware for implementation of Principal Company and Trade Flow realignment leading to multi-million dollar saving to enterprise}
\item
  \textbf{2019 - Outstanding Team Achievement}\newline\textit{India Apex Award for best team, awarded for Unit Business Improvement in profitability and return on assets.}
\item
  \textbf{2018 - Trade Secret: P28429}\newline\textit{Awarded Trade Secret for development of Export Production Planning and Dispatch tool. This leads to reduced demurrage charges and asset optimization.}
\item
  \textbf{2017 - Enterprise Asset Project of the Year}\newline\textit{Global award for Leading Multimillion Dollar asset optimization across India and US Factory Supply Chain}
\item
  \textbf{2010 - CEO Award and President Award}\newline\textit{Global Enterprise award for new product introduction}
\end{itemize}

\hypertarget{education}{%
\section{Education}\label{education}}

\textbf{POST GRADUATE DIPLOMA IN DATA SCIENCE}\hfill   \textit{May-2018 \hspace{2mm}- \hspace{2mm}Nov-2019}\newline National
Institute of Security Management \& Mumbai
University\newline \textit{One year dimploma in Data Science including statistics and econometrics, machine learning and behavioural analytics. \textbf{Secured 2nd Rank in the course.}}\newline \newline
\textbf{POST GRADUATE DIPLOMA IN BUSINESS MANAGEMENT}\hfill   \textit{Jan-2010 \hspace{2mm}- \hspace{2mm}Feb-2012}\newline Symbiosis
International
University\newline \textit{Two year comprehensive Business Management Diploma by Symbiosis University, a top university for management studies in India. \textbf{Secured 1st Rank in the course.}}\newline \newline
\textbf{BACHELOR OF ENGINEERING}\hfill   \textit{Jun-1999 \hspace{2mm}- \hspace{2mm}May-2003}\newline Pune
University\newline \textit{Mechanical Engineering Graduate Degree with honors. \textbf{Ranked in top 10\%}}\newline \newline

\end{document}
