---
name: Rahul Kale
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BE-Mech, PGDBM, PGDDS
position: General Manager, Factory Order Fulfillment, John Deere India Pvt. Ltd.
address: Pune, India
phone: +91 77708 11127
email: rahul.kale@gmail.com
# website: 
github: r-kale
linkedin: rahul-kale-723a0720
twitter: rahulvilaskale
docname: Resume
headcolor: 414141
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
googlesheets4::gs4_deauth()
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

# Education

```{r education}
googlesheets4::read_sheet(
  "https://docs.google.com/spreadsheets/d/1s0jXD3LGOmCZnaT0He1ibfQi9Kf9AqE9d_s0_L3eNIo",
  sheet = "education"
  ) %>% detailed_entries(uni, dates, degree, loc, details)
```

# Assignments
## A Brief Timeline
\footnotesize
In John Deere, I have had the fortune to work in multiple functions in various capacities and also in all the manufacturing facilities, Pune, Dewas *(I relocated there)* and Sirhind factories.  
The other significant aspect of my career has been the privilege to explore multiple facets of the functions; developing components at one end and developing factory sourcing at another.  
The journey continues...

```{r assignments}
googlesheets4::read_sheet(
  "https://docs.google.com/spreadsheets/d/1s0jXD3LGOmCZnaT0He1ibfQi9Kf9AqE9d_s0_L3eNIo",
  sheet = "employment"
  ) %>% 
  arrange(desc(when)) %>% 
  mutate(when = paste0(when," : ")) %>% 
  brief_entries(glue::glue("\\textbf{<role>}: \\newline <details>", .open = "<", .close = ">"), when, with = area,.protect = FALSE)
```

\newpage
# Leadership Experience
## Few important learnings
\footnotesize
Each of my assignments brought me new learning and opportunities to apply skills gained along the way. I want to highlight few of those learning.

```{r leadership_experience}
googlesheets4::read_sheet(
  "https://docs.google.com/spreadsheets/d/1s0jXD3LGOmCZnaT0He1ibfQi9Kf9AqE9d_s0_L3eNIo",
  sheet = "leadership_experience"
  ) %>% 
  arrange(desc(to),group_rank) %>%
  mutate(to = as.character(to)) %>% 
  mutate(to = case_when(to == "2020" ~ "Current",
                        TRUE ~ to)) %>% 
  mutate(when = paste0(from," - ",to )) %>% 
  detailed_entries(what,when,with,where,why,.protect = FALSE)

```

# Work Experience

```{r work_experience}
googlesheets4::read_sheet(
  "https://docs.google.com/spreadsheets/d/1s0jXD3LGOmCZnaT0He1ibfQi9Kf9AqE9d_s0_L3eNIo",
  sheet = "work_experience") %>% 
  arrange(desc(last_held),group_rank) %>% 
  detailed_entries(what = glue::glue("\\textbf{<what>} : \\textit{<dept> - <exp>}",.open = "<",.close = ">"),why = why,.protect = FALSE)
```

# Digitization Potential
## Working with Data
With technology and data being increasingly accessible, leveraging these offer tremendous opportunities in changing the way we work, bringing in a completely new paradigm, enabling us to ask questions and expect ***reproducible and repeatable*** answers to those questions.  
Seeing the potential of data in my area of work, I am working on driving progress in this exciting domain.  
Here is summary of the work initiated in OFP:

```{r data}
googlesheets4::read_sheet(
  "https://docs.google.com/spreadsheets/d/1s0jXD3LGOmCZnaT0He1ibfQi9Kf9AqE9d_s0_L3eNIo", sheet = "data") %>%
  detailed_entries(what =  glue::glue("\\textbf{<step>}",.open = "<",.close = ">"), why = details,.protect = FALSE)

```

# Distinctive Mentions

```{r distinctive_mentions}
googlesheets4::read_sheet(
  "https://docs.google.com/spreadsheets/d/1s0jXD3LGOmCZnaT0He1ibfQi9Kf9AqE9d_s0_L3eNIo", sheet = "distinctive_mentions") %>%
  arrange(desc(year)) %>% 
  brief_entries(what = glue::glue("\\textbf{<mention>} \\newline <details>",.open = "<",.close = ">"), when = year,.protect = FALSE)

```

# Intrests

```{r intrests}

```


