%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Rahul Kale}{}

\position{General Manager, Factory Order Fulfillment, John Deere India Pvt. Ltd.}
\address{Pune, India}

\mobile{+91 77708 11127}
\email{\href{mailto:kalerahul@johndeere.com}{\nolinkurl{kalerahul@johndeere.com}}}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

% Templates for detailed entries
% Arguments: what when with where why
\usepackage{etoolbox}
\def\detaileditem#1#2#3#4#5{%
\cventry{#1}{#3}{#4}{#2}{\ifx#5\empty\else{\begin{cvitems}#5\end{cvitems}}\fi}\ifx#5\empty{\vspace{-4.0mm}}\else\fi}
\def\detailedsection#1{\begin{cventries}#1\end{cventries}}

% Templates for brief entries
% Arguments: what when with
\def\briefitem#1#2#3{\cvhonor{}{#1}{#3}{#2}}
\def\briefsection#1{\begin{cvhonors}#1\end{cvhonors}}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {August, 2020}
    {Rahul Kale~~~·~~~Resume}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\detailedsection{\detaileditem{Pune University}{June. 1999 - May. 2003}{Bachelor of Engineering}{Pune, India}{\item{Completed my Mechanical Engineering degree with overall First Class with Distinction grade, Secured 71.9\% in the degree examination, 7th in a class of 74 students.}\item{Research Project included product (tool changer) design and development for a educational CNC lathe machine}}\detaileditem{Symbiosis International University}{Jan. 2010 - Feb. 2012}{Post Graduate Diploma in Business Management}{Pune, India}{\item{A two year comprehensive Business Management Diploma by Symbiosis University, a top university for management studies in India}\item{Studied a range of subjects covering Supply Chain, Operation Management \& Financial Management securing 1st Rank in the course.}\item{Course project included defining supply management strategy, new supplier onboarding and development for John Deere Sirhind Works.}}\detaileditem{National Institute of Security Management \& Mumbai University}{May. 2018 - Nov. 2019}{Post Graduate Diploma in Data Science}{Mumbai, India}{\item{Studied a broad collection of units covering many aspects of data science. I learned data manipulation, statistics and econometrics, machine learning and behavioural analytics, securing 2nd Rank in the course with First Class and 81.25\% marks.}\item{My course project included developing product recommendation system for old obsolete products with closest equivalent current products based on machine learning}}}

\hypertarget{assignments}{%
\section{Assignments}\label{assignments}}

\hypertarget{a-brief-timeline}{%
\subsection{A Brief Timeline}\label{a-brief-timeline}}

\footnotesize

In John Deere, I have had the fortune to work in multiple functions in various capacities. In these assignments, in addition to Pune factory, I could work with Dewas \emph{(I relocated there)} and Sirhind factories while they were still being constructed.\\
The other significant aspect of my career has been the privilege to explore multiple facets of the functions; developing components at one end and developing factory sourcing at another.\\
The journey continues\ldots{}

\briefsection{\briefitem{\textbf{India Factory OF Manager}: \newline Lead the Factory OF for Pune, Dewas and Sirhind.}{2016 : }{Order Fulfillment.}\briefitem{\textbf{Factory SM Manager}: \newline Setup the process and build team for starting the Dewas Tractor Factory.}{2013 : }{Supply Chain.}\briefitem{\textbf{Factory SM Manager}: \newline Lead the Factory OF Supply Chain in Dewas.}{2013 : }{Supply Chain.}\briefitem{\textbf{Development Lead}: \newline Lead the Supply Chain Sheet Metal and Fabrication Commodity.}{2010 : }{Supply Chain.}\briefitem{\textbf{Development Lead}: \newline Lead the Harvester Project as part of Supply Chain including localization of the machine in Sirhind.}{2010 : }{Supply Chain.}\briefitem{\textbf{Manufacturing Project Lead}: \newline Lead for the Krish Project for Manufacturing Engineering, an introduction of a new product family with over 7 million USD budget. This project presented a rare opportunity to work with complete product development cycle from conception to Start of Production.}{2006 : }{Mfg. Engg.}\briefitem{\textbf{Industrial Engineer}: \newline Lead implementation of WPlanner, a time study tool in John Deere Pune Works.}{2005 : }{Mfg. Engg.}\briefitem{\textbf{Line Design}: \newline Selected as Management Trainee, a fast track program in L\&T. Introduced new manufacturing stations and worked on capacity and line design.}{2004 : }{Mfg. Engg.}\briefitem{\textbf{OFP Buyer}: \newline Joined as a fresh Graduate with L\&T - John Deere, responsible for hardware and sheet metal procurement.}{2003 : }{Supply Chain.}}

\hypertarget{leadership-experience}{%
\section{Leadership Experience}\label{leadership-experience}}

\hypertarget{few-important-learnings}{%
\subsection{Few important learnings}\label{few-important-learnings}}

\footnotesize

Each of my assignments brought me new learning and opportunities to apply skills gained along the way. I want to highlight few of those learning.

\detailedsection{\detaileditem{Managing through COVID}{2020 - Current}{Managing Disruption}{Order Fulfillment}{\item{Pune Factory restarted in early May while Dewas and Sirhind in late April. All the factories had closed in late March. This was a disruption of ~40+ days (lockdown period).}\item{Maintaining team engagement in lockdown period with regular communication , supporting them through home working, and ensuring meaningful projects.}\item{Develop scenario planning to work through resumption plans of factory and arrive at optimum market commitments and factory stretch. Execute the plan and reconcile  with on-the-ground challenges.}\item{While we have lot to learn, the pandemic is a humbling experience which teaches us to look at how we have optimized our businesses and potential of disruptions due to black swan events}}\detaileditem{Digital Transformation}{2016 - 2019}{Lead change management}{Order Fulfillment}{\item{Recognizing the urgent need to move away from traditional processes such as manual excel based planning to overcome the challenges of {\textit{one version of truth, inefficiencies in scaling, lack of reproducibility and making the process {\textbf{vulnerable to increasing complexity.}}}}}\item{Overcoming the questions of {\textit{why-break-a-working-system, this-increases-work, and why-learn-something-new}}}\item{My learnings: Start small and with step by step approach, drive smaller changes first or easy wins enabling all to see benefits of change.}}\detaileditem{Strategy and Execution}{2013 - 2016}{Build for future}{Supply Chain}{\item{I was the OF Supply Chain lead in Dewas during the start-up phase for this group-up new facility.}\item{In this role, I was responsible to develop procurement and warehouse strategy and process for Dewas OF Supply Chain. In addition to setting up the procurement process I got the opportunity to define raw inventory accuracy}\item{Among the highlights of the Dewas OF SM is 100\% raw material warehouse operations outsourcing. This is the only facility in India where this is implemented.}\item{I continued working in Dewas beyond the startup phase and successfully executed SM operations for a total of 3 years. We also had the satisfaction of completing the comprehensive Internal Control Audit in Dewas with high score and no unfavourable remarks.}}\detaileditem{Navigating unknown challenges}{2010 - 2013}{Establish Supply Base}{Supply Chain}{\item{In my first job in managerial role I was responsible for new part development in sheet metal commodity, tooling development, costing and price settlement. I was also responsible from Supply Chain side for start-up of Grain Harvester facility at Sirhind}}\detaileditem{Establish Supply Base}{2010 - 2013}{Navigating unknown challenges}{Supply Chain}{\item{Sirhind facility was the first endeavour for bringing in {\textit{a Grain Harvester}} ,in India from John Deere other than tractors. The project involved rapid localization of parts and implementation of, {\textit{kitting process from China}} ,for other remaining parts.}\item{The novelty involved in this activity was exceptionally high compared to other localization due to a novel product and design requirements.}\item{Me and my team was responsible for scouting supply base for sourcing of the new complexity introduced by Harvesters, developing the suppliers and onboarding them. We developed sources for complex sheet metal tooling, designing and executing the localization.}\item{I worked with the China sourcing team for consolidating the common parts which were not part of immediate localization efforts. We onboarded a new supplier to consolidate the parts from the supply base, do quality checks and follow a import schedule.}}\detaileditem{Creating trust}{2006 - 2010}{Influencing}{Manufacturing Engineering}{\item{I was responsible for implementation of two critical projects: the first was implementation of new time standard on Pune assembly lines and the second was leading the Manufacturing Design subprocess for the EPDP program for 5C tractor platform.}\item{For the implementation of time standard, I had the opportunity to work on a new tool {\textit{WPlanner}} and interact with the workforce, explaining them the changes in work standard which would impact the work pace.}\item{While working as the lead for Manufacturing Design subprocess on 5C product line introduction, I worked with my colleagues to ensure the activity of capital procurement, line design, workstation changes were executed as per project expectations and timeline}\item{Both the projects involved working as a individual contributor while working with multiple stakeholders. This phase taught me the importance of building relationships, developing trust and credibility and acting in fair and transparent manner to be successful in executing the goals.}}}

\hypertarget{work-experience}{%
\section{Work Experience}\label{work-experience}}

\detailedsection{\detaileditem{\textbf{Sales and  Operation Planning} : \textit{Order Fulfillment - 5+ years}}{}{}{}{\item{Lead a team of planning engineers for doing Sales and Operation Planning for Pune, Dewas and Sirhind factories in India. Planning involves domestic India forecast for rolling 18 month and working with stakeholders for export planning. Manage annual volume of 100K tractors with 20K+ DT aggregates among other interfactory parts}}\detaileditem{\textbf{Production Planning and Control} : \textit{Order Fulfillment - 5+ years}}{}{}{}{\item{Guide the team for day to day production planning, guiding on balancing constraints and executing control}}\detaileditem{\textbf{Product Configuration \& Complexity Management} : \textit{Order Fulfillment - 5+ years}}{}{}{}{\item{Guide the team to develop complexity index, understand pruning of portfolio to limit variant proliferation and for new EPDP projects work on creating variant configurations}}\detaileditem{\textbf{Complete Goods Asset Management} : \textit{Order Fulfillment - 5+ years}}{}{}{}{\item{Develop targets and band charts for Finished Good Inventory, execute control to manage the Inventory. Work with finance to manage aging of FG and appropriate liquidation plans. Work with stakeholders for PxP DOH targets and control.}}\detaileditem{\textbf{Factory Leadership Council Member} : \textit{Order Fulfillment - 5+ years}}{}{}{}{\item{Participate and Contribute in Factory Leadership Council on strategic planning and initiatives, long term planning, annual goal setting among other.}}\detaileditem{\textbf{Direct Material Procurement} : \textit{Supply Chain Management - 6+ years}}{}{}{}{\item{Leading a team of buyers for establishing and executing procurement policies and managing procurement with diverse and international Supply Base for commodities including Sheet Metal, Electrical, Hydraulic, Castings and Machining, Gear and Shafts, Hardware, Oil and Coolants among others. Managing annual procurement in excess of m\$100.}\item{Leading warehouse staff for working through warehouse plans including designing layouts and storage systems, replenishment systems, Kanban or 2-bin systems. Defining material handling needs and working on optimum layouts for reducing congestion. Management of Docks and receipt planning. Designing transport storage systems for optimized logistics cost.}}\detaileditem{\textbf{Inventory Management and Control} : \textit{Supply Chain Management - 6+ years}}{}{}{}{\item{Defining Inventory DOH targets, SAP MRP parameters, and working with suppliers and buyers to optimize procurement and minimize inventory. Defining Cycle count process based on ABC categorization and ensuring inventory accuracy.}}\detaileditem{\textbf{Part Development} : \textit{Supply Chain Management - 6+ years}}{}{}{}{\item{Leading team of PDP SM engineers for managing development lifecycle from design drawings to PPAP of Sheet Metal components.}\item{Defining costing norms, doing should-cost analysis and settling part cost with suppliers. Working on tool design, production process and establishing quality norms for regular procurement.}}\detaileditem{\textbf{Line Design} : \textit{Manufacturing Engineering - 5+ years}}{}{}{}{\item{As a Industrial Engineer define line or station layout, work content, conduct time study and establish work norms.}\item{Engage with indirect suppliers for procurement of tools, machine and equipments for capital purchase and establish required manufacturing capacity.}\item{Work on EPDP process and Manufacturing Design engineer and lead through completion of all program execution phases.}}}

\hypertarget{digitization-potential}{%
\section{Digitization Potential}\label{digitization-potential}}

\hypertarget{working-with-data}{%
\subsection{Working with Data}\label{working-with-data}}

Increasingly technology and data have become more accessible. Leveraging these offer tremendous opportunities in changing the way we work, bringing in a completely new paradigm, enabling us to ask questions and expect \emph{reproducible and repeatable} answers to those questions.\\
Seeing the potential of data in my area of work, i embarked on completing my Post Graduation in Data Science to help learn and drive progress in this exciting domain.\\
Here is summary of the work initiated in OFP:

\detailedsection{\detaileditem{\textbf{Data Pipeline}}{}{}{}{\item{With data being generated with every transaction, it is important to think about how accessible is the data, is the process generating it consistent, what is the refresh cycle and the ease with which we can use it.}\item{Before embarking on our journey of a digital OF, we worked on developing strong underlying process to ensure our data capturing is consistent.}\item{We leveraged the SAP - HANA sidecar for accessing the data our process generate.}\item{This is a very significant portion of the digitization journey and takes time. We established and ingrained the new processes into our work culture abalbing a high degree of reliance on the underlying data and it's reliability; making it reproducible and repeatable.}}\detaileditem{\textbf{Replace}}{}{}{}{\item{Bringing in change is difficult, especially so if you are trying to make reports automated which were painstakingly generated by individuals.}\item{To make the process smooth and make sure we develop trust on the new system, we started replacing one report at a time, deploying automated reports in-parallel.}\item{I leveraged R - open source programming language to connect the data and work with it to deliver majority of the reports, deploying programmers where necessary.}\item{Majority of our reports were changed with this process; some example include our OFP summary production and shipment summary report, order bank reports, configuration process preparation reports, production control reports etc.}}\detaileditem{\textbf{Innovate}}{}{}{}{\item{With the reports automated, focus was on going beyond summary and asking more analytics out of the data.}\item{One area which is of particular pain to us was India domestic Shipment forecast.}\item{I leveraged historical sales to generate rolling sales forecast utilizing multiple forecasting models and ensembling the results.}\item{Another area was to identify current equivalent products for the old obsolete ones. I deployed clustering approach using machine learning algorithm to automate this process.}\item{A third example is deployment of SAP - IBP tool, a first in Deere for making our S\&OP process capable, fast and structured.}\item{We will continue to work on innovate-report-innovate cycle through multiple other reports}\item{These anlaytic cycle help business bring in structure and advantage.}\item{The last aspect is to take generation process out of the cycle to make the deployed analytics autonomous. This is done leveraging markdown and data visualization}}\detaileditem{\textbf{Potential}}{}{}{}{\item{This approach converts the traditional process where focus is on as-is status reports to focus on asking meaningful what-if questions and make the data provide answers - in a reproducible and repeatable way.}}\detaileditem{\textbf{My skills}}{}{}{}{\item{Understanding of Data Science, leveraging the same for Business Analytics and lead transformation projects.\hspace*{\fill} {\textit{ - High to Expert.}}}\item{R Langauage for analytics, visualization and reporting. \hspace*{\fill}  {\textit{- Moderate.}}}\item{Tableau for data visualizaton and reports. \hspace*{\fill}  {\textit{- Moderate to Expert.}}}\item{MS Excel. \hspace*{\fill}  {\textit{- Expert.}}}\item{Python Programming Language. \hspace*{\fill}  {\textit{- Beginner.}}}\item{This resume is programatically generated using R-langaue and RMarkdown. Data is in stored in a googlesheet, making the generation process repeatable for updates.}}}

\hypertarget{distinctive-mentions}{%
\section{Distinctive Mentions}\label{distinctive-mentions}}

\briefsection{\briefitem{\textbf{2019 President Award of Excellence} \newline Trade Flow Realignment Project}{2019}{}\briefitem{\textbf{Outstanding Team Achievement} \newline Dewas Business Improvement Team}{2019}{}\briefitem{\textbf{Trade Secret: P28429} \newline Export Production Planning and Dispatch tool.}{2018}{}\briefitem{\textbf{A\&T Asset Project of the Year} \newline m\$ 40+ reduction in assets in Pune, Augusta and EU}{2017}{}\briefitem{\textbf{CEO Award} \newline 5C Platform introduction in India}{2010}{}\briefitem{\textbf{2010 President Award of Excellence} \newline 5C Platform introduction in India}{2010}{}}

\end{document}
